---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Principal Components Difference-in-Differences

<!-- badges: start -->
<!-- badges: end -->

pcdid implements factor-augmented difference-in-differences (DID) estimation. It is useful in situations where the user suspects that trends may be unparallel and/or stochastic among control and treated units. The data structure is similar to that in a DID setup.

The estimation method is regression-based and can be considered as an extension of conventional DID regressions. pcdid also implements a parallel trend alpha test (based on an interactive effects structure) and a recursive procedure that determines the number of factors automatically.

For further details, please see Chan and Kwok (2022) who developed the pcdid approach and the alpha test.

## Installation

You can install the development version of pcdid from [GitHub](https://github.com/) with:

``` r
devtools::install_github("adamwang15/pcdid")
```

## Example

This is a basic example which replicates Chan and Kwok (2022)

```{r example}
library(pcdid)

result <- pcdid(
  lncase ~ treated + treated_post + afdcben + unemp + empratio + mon_d2 + mon_d3 + mon_d4,
  index = c("state", "trend"),
  data = welfare,
  alpha = TRUE
)
```

To access the mean-group estimates

```{r}
result$mg
```

To access the alpha test result

```{r}
result$alpha
```

To access list of treated unit estimates

```{r}
result$treated
```

To access list of control unit estimates

```{r}
result$control
```
